Life in the canopy: Community trait assessments reveal substantial functional diversity among fern epiphytes

### 2020-01-14 ms/manuscript.Rmd
Put all library() calls in setup.R
and arrange alphabetically

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, cache = FALSE)
library(drake)
library(gt)
library(patchwork)
library(knitr)
library(kableExtra)
library(magrittr)
library(scales)
library(tidyverse)
library(captioner)
library(jntools)
library(conflicted)

conflict_prefer("expand", "tidyr")
conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, cache = FALSE)
